%\documentclass[journal,10pt]{article}
\documentclass[journal,10pt]{IEEEtran}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{soul} 

\newcommand{\subtask}[1]{\begin{quote}\textbf{#1}\end{quote}}
\newcommand{\hod}{h}
\newcommand{\moh}{m}
\newcommand{\dow}{d}
\newcommand{\dom}{d_m}
\newcommand{\wom}{w_m}
\newcommand{\woy}{w_y}
\newcommand{\yyy}{a}

\newcommand{\IN}{\mathbb{N}}
\newcommand{\defeq}{\coloneqq}

\author{Jan Lippert \(<\)\href{mailto:ljan@mail.upb.de}{ljan@mail.upb.de}\(>\)}
\date{\today}

\begin{document}

\title{Predicting Parking Space Availability in Paderborn}
\maketitle

\begin{abstract}
The Parking Prediction system Paderborn is available at \url{http://pppb.herokuapp.com/}. It was written in Play! Scala and uses the \href{smile}{haifengl.github.io/smile/} library. the system regularly predicts the number of available parking spaces for the ``Libori-Galerie'' 15 minutes in advance.
\end{abstract}

\tableofcontents
\begin{itemize}
  \item Topic introduction
  \begin{itemize}
    \item \st{What question does your work answer}
    \item \st{What related work does exist}
    \item Why did you choose your topic
  \end{itemize}
  \item Methodology choice
  \begin{itemize}
    \item Introduction of chosen methodology\todo{extend section \ref{sec:training_model} by introducting regression trees}
    \item \st{Motivation behind choice}
    \item Discussion of possible problems with data or methodology
    \item Comparison between methodologies, if applicable
    \begin{itemize}
      \item GradientBoost may lead to better results
      \item Add comparison and ``why''
    \end{itemize}
  \end{itemize}
  \item Verification
  \begin{itemize}
  	\item \textbf{TODO. Needs a lot of work!}
  \end{itemize}
  \item Run-time technology
  \begin{itemize}
    \item \st{Introduction of run-time system}
    \item \st{Technology choices and motivation}
    \item Discussion of possible problems with setting up run-time system
  \end{itemize}
  \item Results
  \begin{itemize}
    \item Result of your work (hypothesis statement)
    \item Discussion of prpossible future work
    \item Reflection against existing literature
  \end{itemize}
  \item Reflection
  \begin{itemize}
    \item What did you learn
  \end{itemize}
\end{itemize}






\section{Introduction}

\input{report_lippert_introduction}

\subsection{Related Work}
\input{report_lippert_related_work}


\section{Methodology choice}

Since this work is inspired by \cite{parkendd}, a RegressionTree model was chosen as machine learning method. To keep the complexity of the application in check, the model was kept simple: the data consisted only of timestamped availability data.\todo{explain a little bit more about regression trees}

\subsection{Data Sources}\label{data sources}
\input{report_lippert_data_sources}

\subsection{Hypothesis \& Training Method}\label{sec:training_model}
\input{report_lippert_hypothesis}

\subsection{Discussion of possible problems with data or methodology}\todo{write section}
\subsection{Comparison between methodologies, if applicable}\todo{write section}

\section{Verification}
\input{report_lippert_verification}

%\section{Results}
%\subsection{Result of your work (hypothesis statement)}
%\subsection{Discussion of possible future work}
%\subsection{Reflection against existing literature}



\section{Run-time technology}

It was chosen to develop the web application in Scala using the Play! framework, mainly because of familiarity with the language and its usage in machine learning applications. It is also used in  

\subsection{Architecture}\label{sec:architecture}
\input{report_lippert_technology_architecture}

\subsection{Frameworks}\label{sec:frameworks}
\input{report_lippert_technology_frameworks}

\section{Encountered Problems}\label{sec:challenges}
\subsection{Malfunction of the Parking Guidance System}
\input{report_lippert_asp_malfunction}

\subsection{Heroku Free Limitations}
\input{report_lippert_heroku_free_limitations}



\section{Reflection}
\input{report_lippert_reflection}

\section{Addiotional todos}
\subsection{Model iterations}

Week of month was removed. was not important in training. unsurprising result
\bibliographystyle{ieeetr}  
\bibliography{report_lippert}

\end{document}
