After collecting data for some time, I did some correlation analysis on the data. I noticed that all entries had ``\(\wom = 1\)'' despite the app being online for more than a week. Further investigation showed that the data was only available for 3 different days. 

The reason for this failure was the uninformed use of the Heroku Free package. Free dynos will sleep after 30 minutes minutes of inactivity. After this was noticed, multiple services and workarounds were investigated.

However, most of the workarounds were from before 2015. In 2015, Heroku added the requirement that free dynos need to sleep 6 hours a day. Unfortunately the most promising service -- \url{http://kaffeine.herokuapp.com/} -- is not functional anymore.

To keep the system running, a bash script was created which keeps the dyno awake by sending regular HEAD requests. Since the dyno is still required to sleep 6 hours a day, a sleeping time had be chosen. Luckily, the ``Libori-Galerie'' is closed from 2am to 8am and the dyno will rest in this period. 

Also, there were multiple problems in accessing the database The free tier only allows 20 concurrent connections to the Postgresql database. These connections were exhausted 5 minutes after the start of the application. This could be solved by configuring the application to restricting the number of database connections to 10 -- when the application was configured to use 20 connections, problems persisted.

The next limit is in the size of the database. The free tier only allows \(10000\) rows. Insert actions will be disabled after the database has had more than \(10000\) for 7 days. This challenge will be circumvented by removing old data in regular intervals.